### 2019-08-31 Writeup/Thesis/chapters/lit_review.tex
Changes; - Final check for gramatical errors

An E2EE connection uses the key types discussed previously to exchange messages between verified parties securely. However, this hinges on the verification of the initial parties, if one party impersonates another and receives sensitive communication, the secure encryption is completely circumvented. Therefore, the correct identification of parties is crucial to maintaining security. The exploitation of this is known as a Man-in-the-middle (MiTM) attack. This attack is commonly bidirectional, and if executed correctly, there is often no discerning change to the user experience. Figure \ref{fig:mitm} contains a visual representation of this attack. In the diagram Eve (attacker) is impersonating Alice to Bob and Bob to Alice. Therefore, as both directions of communication are compromised all traffic will route through the attacker Eve.

@@

Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob), the unique aspects of the keys can be used to identify parties. This is achieved succinctly through the use of a fingerprint. A fingerprint is a string of alphanumerical characters that are unique to each key. Therefore the fingerprint of the two respective public keys are different, and, thus can be used for identification.

@@

Historically fingerprints have been represented as a hexadecimal string, whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card. Figure \ref{fig:businessCard} shows an example business card. A user will then use the fingerprint present on the card to compare to the one available on a device. This will have to be performed by each user. This process is known as the \textit{``authentication ceremony.''}

@@

System designers are, however, moving away from the structure of one fingerprint per identity and are now implementing a combined key. This change is due to the assumed increase in usability. Users now compare a single fingerprint together, instead of two sets separately. In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of an SHA-512\footnote{5200 iterations} hash of each parties' identity key, these are then both concatenated together to form a single fingerprint\cite{whatsapp2017paper}. This process produces a unique key per communication pair.

Due to the manual comparison of the fingerprint, length and format are core design considerations. Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}. This shows that comparing complete digests would be cumbersome and error-prone. For example, SHA-1 is 40 hex digits (160-bit) and, therefore, difficult to effectively compare. Therefore, if human interaction is required; there is a need for schemes that work effectively with consideration to human limitations.

@@

\subsubsection*{Text-based schemes}
Encoding schemes are the physical method of encoding used to represent the fingerprint. The most common representation is alphanumerically with either \textbf{Hexadecimal} (0-9/A-F) or \textbf{Base32} (2-7/A-Z). These encoding schemes are the most popular due to their intuitive simplicity and lack of hardware requirements.

Fingerprints can also be encoded using natural language. The fingerprint can be chunked and mapped to a set or words. The same principle can be used to fill placeholders in a pre-defined sentence allowing the simple formation of syntactically accurate English sentences. Moreover, other languages can be used such as Chinese, Japanese or Korean to map fingerprint chunks to characters.

@@

\subsubsection*{Graphical Schemes}
Graphical schemes are a potential alternative to text-based schemes. They often attempt to visualise small changes in the fingerprint to assist in alerting the user to small changes. This schemes should, therefore, be able to provide increased usability and security. This section will explain the relevant schemes in this paper.

@@

\textbf{OpenSSH}. OpenSSH Visual Host Key is an ASCII based graphical scheme used in MiTM detection when connecting to SSH servers. The image is generated by movement of the central marker across a grid. Every 2-bits of the generated MD5 hash defines the diagonal direction of movement. For example, if the first 2-bits are \verb|11| the marker will move South East. The different characters are determined by the number of times the marker is present in that index, for example, if the maker is present on a square 4 times the character will be an equals sign (\verb|=|).

\textbf{Unicorns}\footnote{\url{https://unicornify.pictures/}}. Unicorns can be considered an example of an ``Avatar'' graphical scheme. The provided hash changes aspects of the image such as background colour, horn length and colour of the Unicorn's mane.

\textbf{Vash}\footnote{\url{https://github.com/thevash/vash}}. Vash is similar to that of unicorns where the hash determines certain characteristics of the image. Vash claims to have $\approx 5,438$ bits of entropy.

@@

Research in this area has taken these various encoding schemes and compared their falibility to impersonated attacks. The main elements of comparison have been the ``accuracy of attack detection" and ``time to compare." In this paper, these are considered the metrics of ``security'' and ``usability,'' respectively.

@@

    \item \textbf{Poor precision.} Due to the previously discussed point of a limited code space. \cite{patman2001soundex} re-iterates this point, but in the context of name matching where Soundex's poor performance was demonstrated. Soundex only gained and overall accuracy of 36.37\% when matching names within a provided database.
\end{enumerate}

@@

It also allows for variable-length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex. It was in use right up util the end of 1998 within various US Government departments.

@@

Table \ref{tab:features} contains the mappings used in \cite{parrish2017poetic} to create the phonetic feature lists.
Using this with all 133,852 entries in version 0.7b of the CMU Pronouncing Dictionary, 949 unique properties were produced overall. The author then performed principal components analysis\footnote{Details regarding this process is outside the scope of the project. Please, however, if interested please refer to this resource for more information: \url{http://setosa.io/ev/principal-component-analysis/}} on the unique properties to reduce them down to 50.

@@

\subsubsection*{Encoding scheme performance}
Results 
from the literature consistently show the effectiveness of language-based encodings such as Words or Sentences with accuracies ranging up from 94\% \cite{dechand2016empirical}\cite{tan2017can}\cite{kainda2009usability}. In all cases, these were the best schemes from the sets assessed. The exception to this is the work performed by \textbf{H. Hsiao \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63\%.
\\\\
Aside from textual representations were graphical schemes. As explained in Section \ref{sec:encodingSchemes} the main graphical schemes assessed by the literature were: Random Art, Flag, T-Flag, Vash, OpenSSH Visual Host Key and Unicorns. These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study}. The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
\\
\begin{table}[h!]
    \makebox[\textwidth][c]{
        \input{tables/background/fingerprint_times.tex}
    }%
    \caption{Average comparison time (seconds) for the encoding schemes}
    \label{tab:times}
\end{table}
\\
In terms of usability of graphical schemes, the literature concurred on their high usability. The comparison speed of these schemes were all among the quickest (See Table \ref{tab:times} for an overview of timings). Other work also indirectly agreed with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical, kainda2009usability}.
In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with only two papers available. There is also no overlap in the schemes assessed with each paper reviewing a unique set. This area is, therefore, a promising candidate for further research.

@@

Tables \ref{tab:times} \& \ref{tab:results} contain the accuracy results of all papers assessed; this is to aid in visual comparison. Each paper used a different metric for measuring accuracy. Therefore, all results have been translated into ``overall accuracy.''. For example, if a paper presented "security failures" or "attack success rate" of 5\% the overall accuracy of the scheme is 95\%.

@@

One consideration of note is that made by \textbf{S. Dechand \textit{et al.}}\cite{dechand2016empirical} where they briefly consider medical conditions such as ADHD and reading or visual disorders and the way they affect the comparison's effectiveness. The results highlight a slight reduction in overall accuracy, however, due to their small sample size, the results cannot be considered conclusive. This aspect is unique to all literature assessed. Further work would be required to produce conclusive results. Therefore, highlighting a gap in the literature.

@@

\subsubsection*{Conclusion}
Overall, this review has identified several key areas suitable for further work.
The first is the performance assessment of graphical encoding schemes. Recreation of pre-existing results from \cite{hsiao2009study}\cite{tan2017can} is required to corroborate current conclusions and validate results.
Another gap in the research is the consideration into the utilisation of encoding schemes in realistic conditions, i.e. ``remove vs proximity." This topic was initially covered by \cite{shirvanian2017pitfalls}, but their scope was limited. Further work, therefore, could increase the scope and touch upon a large number of schemes in these settings. The final aspect for further work is the limited consideration into the feasibility of attacks on encoding schemes. All of the papers assessed simulated attacks and had minimal consideration for their execution. Therefore, further work could delve
into the implementation and feasibility of such attacks.

@@

A more specific subsection of textual fingerprints is the use of words and sentences to encode hash digests. Some of the first work in this area was by \textbf{Juola} and \textbf{Zimmermann} \cite{juola1996whole}. Their work aimed to produce a word list where phonetic distinctiveness was prioritised. Each word is mapped to a single byte. The unique aspect of the word list is the separation of ``even'' and ``odd'' words where ``even'' byte indices are sample from the even-list and ``odd'' from the odd-list. This technique effectively creates two sub-word lists.  A genetic algorithm was used to maximise linguistic distance. The paper also includes a study on effective measures of ``linguistic distances'' of words and provided an in-depth discussion into these areas.

Overall the paper provides a foundation for formalising the creation of effective wordlists. A limitation is the lack of empirical data gathered on the performance. However, this was later evaluated in work by \textbf{S. Dechand \textit{et al.}}\cite{dechand2016empirical} and shown to be an effective encoding scheme.

@@

Aside from this research, there have been further informal implementations of fingerprint encodings. The first being by \textbf{Michael Rogers}\footnote{\url{https://github.com/akwizgran/basic-english}}. Rogers' implementation is a program designed to map fingerprints to pseudo-random poems. This implementation was again, empirically evaluated by \textbf{S. Dechand \textit{et al.}}\cite{dechand2016empirical}. Earlier work by \textbf{N. Haller} with the S/KEY\cite{haller1995s} shows the implementation of a system designed to represent a hash as a series of six short words. However, this system is designed for a one-time-password purpose and only provides word mappings for basic human usability of the password and not within a fingerprint verification context. Therefore, the wordlist has not been designed with pronounceability in mind.

@@

Alongside the abnormally high number of words, the design choice to exclude slang and profanities from the English Trustword dictionary requires dual-mapping of a section of words. Approximately 13633/65536 (20.8\%) of words are re-mapped in the dictionary, leaving 51903 unique words. The re-mapping is performed on a alphabetical loop. Figure \ref{fig:remap} shows the position in the dictionary where this occurs.

@@

One of the most significant limitations addressed by the authors  was the reduction in success rates as the size of the authentication string grew. The morphing and re-ordering  attacks become increasingly ineffective as the user had more time to detect imperfections. This aspect is not quantified by the author and the extent of this degradation is never empirically discussed. Therefore, the results from this study are only effective and applicable in a SAS context.

\subsubsection*{Topic Conclusion}
Overall the literature for this subtopic remains sparse and incomplete. Further suggested work could look into the feasibility of generating partial collisions for all textual representations alongside quantified effectiveness on users. With the possibility to concentrate on a few selected implementations. The work would aim to focus on the various physical methods used and their feasibility. This is one area the previous literature has failed to cover and has only theoretically quantified attacker strength without consideration for the actual real-world cost.

@@

In the context of human demographics and the way they alter the performance of the schemes; further research is required into how the fluency of languages affects authentication ceremony. This further work would be a continuation of the initial work by \textbf{H. Hsiao \textit{et al.}}\cite{hsiao2009study} and could allow the creation of schemes that are better suited to specific languages.
Alongside this, there is a research gap in the investigation of how mental impairments affect a schemes performance. This aspect is useful due to the number of potential users being affected. For example, 7\% of the population have been identified as having dyslexic tendencies\cite{peterson2012developmental}. This fact means that with a UK population of around 63,000,000\footnote{From the 2011 Census collated by the Office for National Statistics}  4,410,000 people could benefit from encoding schemes designed to work well with dyslexia. Dyslexia, however, is only one of many impairments that could affect a scheme's performance, thus, contributing to the substantial effect further work could have on this area.

>>>>

An E2EE connection uses the key types discussed previously to exchange messages between verified parties securely. However, this hinges on the verification of the initial parties, if one party impersonates another and receives sensitive communication, the secure encryption is completely circumvented. Therefore, the correct identification of parties is crucial to maintaining security. The exploitation of this is known as a Man-in-the-middle (MiTM) attack. This attack is commonly bidirectional, and if executed correctly, there is often no discerning change to the user experience. Figure \ref{fig:mitm} contains a visual representation of this attack. In the diagram Eve (attacker) is impersonating Alice to Bob and Bob to Alice. Therefore, as both directions of communication are compromised, all traffic routes through the attacker Eve.

@@

Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob), the unique aspects of the keys can be used to identify parties. This is achieved succinctly through the use of a fingerprint. A fingerprint is a string of alphanumerical characters that are unique to each key. Therefore the fingerprint of the two respective public keys are different, and, thus, can be used for identification.

@@

Historically fingerprints have been represented as a hexadecimal string; whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card. Figure \ref{fig:businessCard} shows an example business card. A user then uses the fingerprint present on the card to compare to the one available on a device. This process has to be performed by each user and is known as the \textit{``authentication ceremony.''}

@@

System designers are, however, moving away from the structure of one fingerprint per identity and are now implementing a combined key. This change is due to the assumed increase in usability. Users now compare a single fingerprint together, instead of two sets separately. In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of an SHA-512\footnote{5200 iterations} hash of each parties' identity key; these parts are then concatenated together to form a single fingerprint\cite{whatsapp2017paper}. This process produces a unique key per communication pair.

Due to the manual comparison of the fingerprint, length and format are core design considerations. Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}. These findings show that comparing complete digests would be cumbersome and error-prone. For example, SHA-1 is 40 hex digits (160-bit) and, therefore, difficult to effectively compare. Therefore, if human interaction is required; there is a need for schemes that work effectively with consideration to human limitations.

@@

\subsubsection*{Text-based schemes}
Encoding schemes are the physical method of encoding used to represent the fingerprint. The most common representation is alphanumerical with either \textbf{Hexadecimal} (0-9/A-F) or \textbf{Base32} (2-7/A-Z). These encoding schemes are the most popular due to their intuitive simplicity and lack of hardware requirements.

Fingerprints can also be encoded using natural language. The fingerprint can be chunked and mapped to a set of words. The same principle can be used to fill placeholders in a pre-defined sentence allowing the simple formation of syntactically correct English sentences. Moreover, other languages can be used such as Chinese, Japanese or Korean, to map fingerprint chunks to characters.

@@

\subsubsection*{Graphical Schemes}
Graphical schemes are a potential alternative to text-based schemes. They often attempt to visualise small changes in the fingerprint to assist in alerting the user to small changes. This schemes should, therefore, be able to provide increased usability and security. This section explains the relevant schemes discussed later in this paper.

@@

\textbf{OpenSSH}. OpenSSH Visual Host Key is an ASCII based graphical scheme used in MiTM detection when connecting to SSH servers. The image is generated by the movement of the central marker across a grid. Every 2-bits of the generated MD5 hash defines the diagonal direction of movement. For example, if the first 2-bits are \verb|11|, the marker moves South East. The different characters are determined by the number of times the marker is present in that index, for example, if the maker is present on a square 4 times the character is an equals sign (\verb|=|).

\textbf{Unicorns}\footnote{\url{https://unicornify.pictures/}}. Unicorns can be considered an example of an ``Avatar'' graphical scheme. The provided hash changes aspects of the image, such as background colour, horn length and colour of the Unicorn's mane.

\textbf{Vash}\footnote{\url{https://github.com/thevash/vash}}. Vash is similar to that of unicorns, where the hash determines specific characteristics of the image. Vash claims to have $\approx 5,438$ bits of entropy.

@@

Research in this area has taken these various encoding schemes and compared their fallibility to impersonated attacks. The main elements of comparison have been the ``accuracy of attack detection" and ``time to compare." In this paper, these are considered the metrics of ``security'' and ``usability,'' respectively.

@@

    \item \textbf{Poor precision.} Due to the previously discussed point of a limited code space. \cite{patman2001soundex} re-iterates this point but in the context of name matching where Soundex's poor performance was demonstrated. Soundex only gained and overall accuracy of 36.37\% when matching names within a provided database.
\end{enumerate}

@@

It also allows for variable-length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex. It was in use right up until the end of 1998 within various US Government departments.

@@

Table \ref{tab:features} contains the mappings used in \cite{parrish2017poetic} to create the phonetic feature lists.
Using this with all 133,852 entries in version 0.7b of the CMU Pronouncing Dictionary, 949 unique properties were produced overall.

The author then performed principal components analysis\footnote{Details regarding this process are outside the scope of the project. Please, however, if interested please refer to this resource: \url{http://setosa.io/ev/principal-component-analysis/}} on the unique properties to reduce them down to 50.

@@

\subsubsection*{Encoding scheme performance}
Results 
from the literature consistently show the effectiveness of language-based encodings such as Words or Sentences with accuracies ranging up from 94\% \cite{dechand2016empirical}\cite{tan2017can}\cite{kainda2009usability}. In all cases, these were the best schemes from the sets assessed. The exception to this is the work performed by \textbf{H. Hsiao \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63\%.
\\\\
Aside from textual representations were graphical schemes. As explained in Section \ref{sec:encodingSchemes}, the primary graphical schemes assessed by the literature were: Random Art, Flag, T-Flag, Vash, OpenSSH Visual Host Key and Unicorns. These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study}. The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can}, where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
\\
\begin{table}[h!]
    \makebox[\textwidth][c]{
        \input{tables/background/fingerprint_times.tex}
    }%
    \caption{Average comparison time (seconds) for the encoding schemes}
    \label{tab:times}
\end{table}
\\
In terms of usability of graphical schemes, the literature concurred on their high usability. The comparison speed of these schemes were all among the quickest (See Table \ref{tab:times} for an overview of timings). Other work also indirectly agreed with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical, kainda2009usability}.
In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with only two papers available. There is also no overlap in the schemes assessed with each paper reviewing a unique set. This area is, therefore, a promising candidate for further research.

@@

Tables \ref{tab:times} \& \ref{tab:results} contain the accuracy results of all papers assessed; this is to aid in visual comparison. Each paper used a different metric for measuring accuracy. Therefore, all results have been translated into ``overall accuracy.''. For example, if a paper presented "security failures" or "attack success rate" of 5\%, the overall accuracy of the scheme is 95\%.

@@

One consideration of note is that made by \textbf{S. Dechand \textit{et al.}}\cite{dechand2016empirical} where they briefly consider medical conditions such as ADHD and reading or visual disorders and the way they affect the comparison's effectiveness. The results highlight a slight reduction in overall accuracy; however, due to their small sample size, the results cannot be considered conclusive. This aspect is unique to all literature assessed. Further work would be required to produce conclusive results. Therefore, highlighting a gap in the literature.

@@

\subsubsection*{Conclusion}
Overall, this review has identified several key areas suitable for further work.
The first is the performance assessment of graphical encoding schemes. Recreation of pre-existing results from \cite{hsiao2009study}\cite{tan2017can} is required to corroborate current conclusions and validate results.
Another gap in the research is the consideration into the utilisation of encoding schemes in realistic conditions, i.e. ``remove vs proximity." This topic was initially covered by \cite{shirvanian2017pitfalls}, but their scope was limited.

Further work, therefore, could increase the scope and touch upon a large number of schemes in these settings. The final aspect for further work is the limited consideration into the feasibility of attacks on encoding schemes. All of the papers assessed simulated attacks and had minimal consideration for their execution. Therefore, further work could delve
into the implementation and feasibility of such attacks.

@@

A more specific subsection of textual fingerprints is the use of words and sentences to encode hash digests. Some of the first work in this area was by \textbf{Juola} and \textbf{Zimmermann} \cite{juola1996whole}. Their work aimed to produce a word list where phonetic distinctiveness was prioritised. Each word is mapped to a single byte. The unique aspect of the word list is the separation of ``even'' and ``odd'' words. Even byte indices are sampled from the even-list and odd indices from the odd-list. This technique effectively creates two sub-word lists.  A genetic algorithm was used to maximise linguistic distance. The paper also includes a study on effective measures of ``linguistic distances'' of words and provided an in-depth discussion into these areas.

Overall the paper provides a foundation for formalising the creation of useful wordlists. A limitation is the lack of empirical data gathered on the performance. However, this was later evaluated in work by \textbf{S. Dechand \textit{et al.}}\cite{dechand2016empirical} and shown to be an effective encoding scheme.

@@

Aside from this research, there have been further informal implementations of fingerprint encodings -- The first being by \textbf{Michael Rogers}\footnote{\url{https://github.com/akwizgran/basic-english}}. Rogers' implementation is a program designed to map fingerprints to pseudo-random poems. This implementation was again, empirically evaluated by \textbf{S. Dechand \textit{et al.}}\cite{dechand2016empirical}. Earlier work by \textbf{N. Haller} with the S/KEY\cite{haller1995s} shows the implementation of a system designed to represent a hash as a series of six short words. However, this system is designed for a one-time-password purpose and only provides word mappings for basic human usability of the password and not within a fingerprint verification context. Therefore, the wordlist has not been designed with pronounceability in mind.
Aside from this research, there have been further informal implementations of fingerprint encodings  The first being by \textbf{Michael Rogers}\footnote{\url{https://github.com/akwizgran/basic-english}}. Rogers' implementation is a program designed to map fingerprints to pseudo-random poems. This implementation was again, empirically evaluated by \textbf{S. Dechand \textit{et al.}}\cite{dechand2016empirical}. Earlier work by \textbf{N. Haller} with the S/KEY\cite{haller1995s} shows the implementation of a system designed to represent a hash as a series of six short words. However, this system is designed for a one-time-password purpose and only provides word mappings for basic human usability of the password and not within a fingerprint verification context. Therefore, the wordlist has not been designed with pronounceability in mind.

@@

Alongside the abnormally high number of words, the design choice to exclude slang and profanities from the English Trustword dictionary requires dual-mapping of a section of words. Approximately 13633/65536 (20.8\%) of words are re-mapped in the dictionary, leaving 51903 unique words. The re-mapping is performed on an alphabetical loop. Figure \ref{fig:remap} shows the position in the dictionary where this occurs.

@@

One of the most significant limitations addressed by the authors  was the reduction in success rates as the size of the authentication string grew. The morphing and re-ordering  attacks become increasingly ineffective as the user had more time to detect imperfections. The author does not quantify this aspect, and the extent of this degradation is never empirically discussed. Therefore, the results from this study are only practical and applicable in a SAS context.

\subsubsection*{Conclusion}
Overall the literature for this subtopic remains sparse and incomplete. Further suggested work could look into the feasibility of generating partial collisions for all textual representations alongside quantified effectiveness on users. The work would aim to focus on the various physical methods used and their feasibility. This is one area the previous literature has failed to cover and has only theoretically quantified attacker strength without consideration for the actual real-world cost.

@@

In the context of human demographics and the way they alter the performance of the schemes; further research is required into how the fluency of languages affects authentication ceremony. This further work would be a continuation of the initial work by \textbf{H. Hsiao \textit{et al.}}\cite{hsiao2009study} and could allow the creation of schemes that are better suited to specific languages.
Alongside this, there is a research gap in the investigation of how mental impairments affect the performance of a scheme. This aspect is useful due to the number of potential users being affected. For example, 7\% of the population have been identified as having dyslexic tendencies\cite{peterson2012developmental}. This fact means that with a UK population of around 63,000,000\footnote{From the 2011 Census collated by the Office for National Statistics}  4,410,000 people could benefit from encoding schemes designed to work well with dyslexia. Dyslexia, however, is only one of many impairments that could affect a scheme's performance, thus, contributing to the substantial effect further work could have on this area.

### 2019-08-31 Writeup/Thesis/chapters/research_question.tex
Changes; - TTS run over the entire paper and corrections added
Changes; - Final check for gramatical errors

    \caption{Most recent RFC security recommendation}
    \label{fig:trustwordsNum}
\end{figure}
\end{center}
By sampling the \pep documentation they have defined the use case of the Trustword handshake: \textit{``A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g. in person or by phone)''.}\footnote{\url{https://www.pep.security/docs/general\_information.html\#handshake}}. It can be assumed due to the increased globalisation of the planet that the most common handshake occurrence is over the phone, and, therefore, not in person. This is the assumed context of the handshake. This means, to create near-matches, the similarity of words is quantified phonetically instead of visually.

@@

    \item What are the time and computation complexity required to generate a 'similar' keys for a targeted key pair? \label{goal:complexity}

>>>>

    \caption{Most recent RFC security recommendation}
    \label{fig:trustwordsNum}
\end{figure}
\end{center}
By sampling the \pep documentation, they have defined the use case of the Trustword handshake: \textit{``A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g. in person or by phone)''.}\footnote{\url{https://www.pep.security/docs/general\_information.html\#handshake}}. It can be assumed due to the increased globalisation of the planet that the most common handshake occurrence is over the phone, and, therefore, not in person. This is the assumed context of the handshake. This means, to create near-matches, the similarity of words is quantified phonetically instead of visually.

@@

    \item What is the time and computation complexity required to generate a 'similar' keys for a targeted key pair? \label{goal:complexity}
